### 2014-09-08 presentation/GAME_HARD_01_PRESENTATION_CONCLUSION.tex
Authored draft future work material under section CONCLUSION.

% Investigate potential memory bandwidth bottleneck
% Establish what the flaws of using WARP are
% Potential use-case: the acceleration of graphics in some virtual platforms
% Double floating point precision
% Complex kernel experiment

>>>>

\begin{enumerate}
\item Microsoft speculates memory bandwidth as a potential bottleneck for throughput-oriented workloads on latency-oriented systems
\item Investigate the performance of WARP in coagency with more complex workloads
\item For brevity, establish whether or not there may be precisional discrepency in double floating point precision
\end{enumerate}

A potential use-case worthy of investigating may be using WARP-like technologies for the purposes of accelerating graphics in virtual platforms.
